Spatial Reasoning and Statistical Graphics

### 2014-10-16 Paper/Draft1/TestingVisualAptitude.Rnw
Allow tidying of code, load xtable at the beginning.

opts_chunk$set(fig.path='Figure/fig-', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, fig.show='hold', par=TRUE, cache=F, concordance=TRUE, autodep=TRUE, root.dir="../")
datadir <- "../../Data/"
imgdir <- "Figure/"
codedir <- "../../Code/"

@@

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
suppressMessages(library(gridExtra))
source(paste(codedir, "Analysis.R", sep=""))
@

>>>>

opts_chunk$set(fig.path='Figure/fig-', cache.path='cache/', fig.align='center', fig.width=5, fig.height=5, fig.show='hold', par=TRUE, cache=F, tidy=T, concordance=TRUE, autodep=TRUE, root.dir="../", comment="|")
datadir <- "../../Data/"
imgdir <- "Figure/"
codedir <- "../../Code/"

@@

library(reshape2)
suppressMessages(library(ggplot2))
library(plyr)
suppressMessages(library(gridExtra))
library(xtable)
source(paste(codedir, "Analysis.R", sep=""))
@
